disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
clarification.

The \pkg{disaggregation} package is built on Template Model Builder (\pkg{TMB})~\cite{tmb2016}, which is a tool for buidling flexible complex models based on C++. \pkg{TMB} combines the packages CppAD~\cite{bell2012cppad}, for automatic differentiation in C++, Eigen~\cite{guennebaud2010eigen}, a C++ library for linear algebra, and CHOLMOD~\cite{chen2008algorithm}, a package for efficient computation of sparse matrices. The use of these packages allows an efficient implementation of the automatic Laplace approximation~\cite{skaug2006automatic} with exact derivatives. \pkg{TMB} calculates first and second order derivatives of the objective function using automatic differentiation~\cite{griewank2008evaluating}.

>>>>

The \pkg{disaggregation} package is built on Template Model Builder (\pkg{TMB})~\cite{tmb2016}, which is a tool for flexibly building complex models based on C++. \pkg{TMB} combines the packages CppAD~\cite{bell2012cppad}, for automatic differentiation in C++, Eigen~\cite{guennebaud2010eigen}, a C++ library for linear algebra, and CHOLMOD~\cite{chen2008algorithm}, a package for efficient computation of sparse matrices. The use of these packages allows an efficient implementation of the automatic Laplace approximation~\cite{skaug2006automatic} with exact derivatives which gives an approximation to the Bayesian posterior. \pkg{TMB} calculates first and second order derivatives of the objective function using automatic differentiation~\cite{griewank2008evaluating}.
